Optimal Fitting of Planar Curves to Prescribed Constraints

### 2014-02-01 idp/documents/documentation/paper.tex
included some more illustrations from slides in documentation

				% TODO: fairness measure integral is over the arc length of the curve
				% TODO: mention that mvc facilitates describing circular arcs and spirals (constant and linearly changing curvature)
				% TODO: add some illustrations, describe their general behaviour, smoothness

@@

@@

@@

			% TODO: consider structuring and naming this section similarly to the slides
			\subsubsection{Segmentation and Notation}
			\label{section:segmentation_notation}

				%\begin{equation*}
				%	\apply{\phi_i}{t} = \sum_j a_{i,j} \cdot t^j
				%\end{equation*}

				Since the polynomial spline is uniquely determined by the coefficients of each polynomial segment, the optimization domain is a vector consisting of all these coefficients. Let \(m\) be the number of segments that make up the polynomial spline. We will use the functions defined in section \ref{section:parametric_plane_curves} with subscript \(i\) when referring to the \(i\)th segment (\(\apply{\phi_i}{t}\)) and without subscript when referring to the whole spline (\(\apply{\phi}{t}\)). Mapping the parameter \(t\) between the segments and the whole spline works as follows:
				\begin{equation*}
					\apply{\phi}{\frac{i + t}{m}} = \apply{\phi_i}{t}
				\end{equation*}
				That is, the segments are simply laid out consecutively in parameter space, scaled to fit the unit interval, making the parameter mapping function linear and static.

>>>>

				% TODO: fairness measure integral is over the arc length of the curve
				% TODO: mention that mvc facilitates describing circular arcs and spirals (constant and linearly changing curvature)
				% TODO: MEC cannot handle curvature specifications
				% TODO: add some illustrations, describe their general behaviour, smoothness

@@

				\begin{figure}[htbp]
					\centering
					\includegraphics[width=\textwidth]{../content/documentation/fairness_mec.pdf}
					\caption{Minimum Energy Curves}
					\label{figure:minimum_energy_curves}
				\end{figure}

@@

				\begin{figure}[htbp]
					\centering
					\includegraphics[width=\textwidth]{../content/documentation/fairness_mvc.pdf}
					\caption{Minimum Variation Curves}
					\label{figure:minimum_variation_curves}
				\end{figure}

@@

			\subsubsection{Segmentation and Notation}
			\label{section:segmentation_notation}

				We start by considering the segment polynomials that make up the polynomial spline we want to find using optimization. Let \(m\) be the number of segments that make up the polynomial spline and let \(d\) be the degree of each segment polynomial. Then the \(i\)th segment polynomial is given by:
				\begin{equation*}
					\apply{\phi_i}{t} = \sum_{j = 0}^{d} a_{i,j} \cdot t^j
				\end{equation*}
				We will use the functions defined in section \ref{section:parametric_plane_curves} with subscript \(i\) when referring to the \(i\)th segment (\(\apply{\phi_i}{t}\)) and without subscript when referring to the whole spline (\(\apply{\phi}{t}\)). Mapping the parameter \(t\) between the segments and the whole spline works as follows:
				\begin{equation*}
					\apply{\phi}{\frac{i + t}{m}} = \apply{\phi_i}{t}
				\end{equation*}
				That is, the segments are simply laid out consecutively in parameter space, scaled to fit the unit interval, making the parameter mapping function linear and static. Figure \ref{figure:linear_segmentation} shows what the segmentation and parameter mapping look like when using 3 segments.

				\begin{figure}[htbp]
					\centering
					\includegraphics[width=100mm]{../content/common/linear_segmentation.pdf}
					\caption{Linear Segmentation}
					\label{figure:linear_segmentation}
				\end{figure}

				Since the polynomial spline is uniquely determined by the coefficients of each segment polynomial, the optimization domain is the vector consisting of all the coefficients \(a_{i,j}\).
